brados: declarative, programmable object storage

### 2016-05-25 paper.tex
paper: add final graphs to sec3
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure*}[t]
	\centering
	\includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/jewel_v_firefly_v_es.png}
	\caption{The cluster-specific optimizations depend heavily on the hardware and software of the storage system. This caption is quite terrible.}
\end{figure*}
%\begin{figure}[t]
%  \centering
%  \begin{subfigure}[b]{.47\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{experiments/librados-sweep/jewel_ssd.png}
%      \caption{1hr,1k,wr,jewel}
%      \label{fig:vanilla_wr_jewel}
%  \end{subfigure}
%  \begin{subfigure}[b]{.47\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/output.read.60min.1k.png}
%      \caption{1hr,1k,rd,jewel}
%      \label{fig:vanilla_rd_jewel}
%  \end{subfigure}
%  \begin{subfigure}[b]{.47\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{experiments/basic-cls-overhead/output.1024.soft.reset.png}
%      \caption{1hr,1k,cls\_wr,jewel}
%      \label{fig:cls_wr_jewel}
%  \end{subfigure}
%  \begin{subfigure}[b]{.47\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{experiments/librados-sweep/firefly_ssd.png}
%      \caption{1hr,1k,wr,firefly}
%      \label{fig:vanilla_wr_firefly}
%  \end{subfigure}
%  \caption{placeholder.}
%\end{figure}

>>>>

\begin{figure*}[t]
	\centering
	\includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/jewel_v_firefly_v_es.png}
	\caption{The cluster-specific optimizations impact performance... a lot. This caption is quite terrible.}
\end{figure*}

\begin{figure}[t]
      \centering
      \includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/output.read.60min.1k.png}
      \caption{This graph shows that a good choice for writes is also good for reads.}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=1.0\linewidth]{experiments/basic-cls-overhead/output.1024.soft.reset.png}
	\caption{1hr,1k,cls\_wr,jewel: this graph shows the overhead of class}
	\label{fig:cls_wr_jewel}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/jewel-hdd-128b.png}
	\caption{shows that with a HDD, it don't matter if you choose omap!!!!!}
	\label{fig:cls_wr_jewel}
\end{figure}
%\begin{figure}[t]
%  \centering
%  \begin{subfigure}[b]{.47\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{experiments/librados-sweep/jewel_ssd.png}
%      \caption{1hr,1k,wr,jewel}
%      \label{fig:vanilla_wr_jewel}
%  \end{subfigure}
%  \begin{subfigure}[b]{.47\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/output.read.60min.1k.png}
%      \caption{1hr,1k,rd,jewel}
%      \label{fig:vanilla_rd_jewel}
%  \end{subfigure}
%  \begin{subfigure}[b]{.47\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{experiments/basic-cls-overhead/output.1024.soft.reset.png}
%      \caption{1hr,1k,cls\_wr,jewel}
%      \label{fig:cls_wr_jewel}
%  \end{subfigure}
%  \begin{subfigure}[b]{.47\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{experiments/librados-sweep/firefly_ssd.png}
%      \caption{1hr,1k,wr,firefly}
%      \label{fig:vanilla_wr_firefly}
%  \end{subfigure}
%  \caption{placeholder.}
%\end{figure}
